Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 supplement.tex
More dreams in supp

\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{figures/geomAllTasks.png}
\caption{The set of tasks for the geometry domain}
\label{alltasksgeom}
\end{figure}

>>>>

\begin{figure}[htp]
\centering
\includegraphics[width = \textwidth]{figures/geomAllTasks.png}
\caption{The set of tasks for the geometry domain}
\label{alltasksgeom}
\end{figure}

\begin{figure}[htp]
  \begin{center}
  \includegraphics[width = 0.75\textwidth]{figures/moreDreams.png}
  \end{center}
\caption{Another example of compiled figures generated by our method.}\label{moreDreams}
\end{figure}

In Figure~\ref{moreDreams} is another montage with several compiled shapes generated by our
method after some training. While not all are that regular, often offer high
level structure in the latter run while no structure is to be found at the
begining.
